Age-related changes in plant growth and traits

### 2015-04-01 leaflifespan.Rmd
continued work on R scripts - starting to build RA model

accessory <- AccessoryCosts_all
accessory$age2 <- accessory$age
accessory$age <- round(accessory$age, digits=1)
#accessory$PerAccessory <- {
#  select(accessory, Total >0,
#  1 - (accessory$Prop/accessory$Total)
#}

>>>>

accessory <- AccessoryCosts_all
accessory$age2 <- accessory$age
accessory$age <- round(accessory$age, digits=1)
accessory$PrePol_S[which(is.na(accessory$PrePol_S))] <- 0
accessory$Total= (accessory$PrePol_A + accessory$PrePol_S + accessory$PostPol_A + accessory$PD + accessory$Prop)

#accessory$PerAccessory <- {
#  select(accessory, Total >0,
#  1 - (accessory$Prop/accessory$Total)
#}
